---
title: 'Homework 4: Bags, Forests, Boosts, oh my'
author: "Brian Corcoran"
date: "2/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tree)
library(randomForest)
library(MASS)
library(ISLR)
library(tree)
```

## Problem 1

Problem 7 from Chapter 8 in the text. To be specific, please use a sequence of
`ntree` from 25 to 500 in steps of 25 and `mtry` from 3 to 9 for by 1. 

## Answer 1
```{r}
set.seed(1234)
df <- tbl_df(Boston)

for (k in 1:20){
  inTraining <- createDataPartition(df$medv, p = .75, list = F)
  training <- df[inTraining, ]
  testing <- df[-inTraining, ]
  mtry <- c(3:9)
  ntree <- seq(25, 500, len = 20)
  results <- tibble(trial = rep(NA, 140),
  mtry = rep(NA, 140),
  ntree = rep(NA, 140),
  mse = rep(NA, 140)) 
  for(i in 1:7){
    cat(sprintf('Trial: %s, mtry: %s --- %s\n', k, mtry[i], Sys.time()))
    for(j in 1:20){ 
      rf_train <- randomForest(medv ~ .,
                               data = training,
                               mtry = mtry[i],
                               ntree = ntree[j])
      mse <- mean((predict(rf_train, newdata = testing) - testing$medv)^2)
      results[(i-1)*20 + j, ] <- c(k, mtry[i], ntree[j], mse)
    }
  }
  if(exists("results_total")){
  results_total <- bind_rows(results_total, results)
  }
  else(
  results_total <- results
  )
}
```
```{r}
plot(results[results$mtry == '3',]$ntree,results[results$mtry == '3',]$mse, col="red",type="l",xlab = "Number of Trees",ylab = "Test MSE",ylim = c(6,9))
lines(results[results$mtry == '4',]$ntree,results[results$mtry == '4',]$mse, col="orange",type="l")
lines(results[results$mtry == '5',]$ntree,results[results$mtry == '5',]$mse, col="green",type="l")
lines(results[results$mtry == '6',]$ntree,results[results$mtry == '6',]$mse, col="blue",type="l")
lines(results[results$mtry == '7',]$ntree,results[results$mtry == '7',]$mse, col="pink",type="l")
lines(results[results$mtry == '8',]$ntree,results[results$mtry == '8',]$mse, col="yellow",type="l")
lines(results[results$mtry == '9',]$ntree,results[results$mtry == '9',]$mse, col="brown",type="l")
legend(title="mtry","topright",c("3","4","5","6","7","8","9"),col=c("red","orange","green","blue","pink","yellow","brown"),cex=.7,lty=1)
```

## Problem 2

Problem 8 from Chapter 8 in the text. Set your seed with 9823 and split into 
train/test using 50\% of your data in each split. In addition to 
parts (a) - (e), do the following:

1. Fit a gradient-boosted tree to the training data and report the estimated 
test MSE. 
2. Fit a multiple regression model to the training data and report the 
estimated test MSE
3. Summarize your results. 

```{r}
attach(Carseats)
set.seed(9823)
subset<-sample(nrow(Carseats),nrow(Carseats)*0.5)
car.train<-Carseats[subset,]
car.test<-Carseats[-subset,]
```

```{r}
car.model.train<-tree(Sales~.,car.train)
summary(car.model.train)
```
```{r}
plot(car.model.train)
text(car.model.train,pretty=0)
```
```{r}
tree.prediction<-predict(car.model.train,newdata=car.test)
tree.mse<-mean((car.test$Sales-tree.prediction)^2)
tree.mse
```


The Test MSE for full grown Tree is recorded as  2.846447